A Journey from Wild to Textbook Data to Reproducibly Refresh the Wages Data from the National Longitudinal Survey of Youth Database

### 2022-02-18 paper/paper.Rmd
comparison of subsets

>>>>

Figure \ref{fig:compare-subsets} contains summaries of corresponding variables in the two subsets.

```{r compare-subsets, fig.cap = "Comparison of original textbook example with refreshed data: (A) highest grade completed, (B) experience and (C) log wages", fig.width = 9, fig.height = 7, out.width = "100%", cache = FALSE}
```
